Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-11 manuscript.tex
figure from https://github.com/laurentperrinet/2022_UE-neurosciences-computationnelles.git

\includegraphics[width=.7\textwidth]{figures/MainenSejnowski1995.png} % TODO replace by the simulation
\caption{The timing of the spikes produced following the repetition of a step stimuli is less reproducible than that to a noisy stimulus. While this seems paradoxical at first sight, this is due to the use of the same \emph{frozen} noise at each repetition and highlight the highly reproducible pattern of spikes when it is driven by a highly dynamic input. See this \href{https://github.com/laurentperrinet/2022_UE-neurosciences-computationnelles/blob/master/C_MainenSejnowski1995.ipynb}{notebook} for a replication of this result using a simple LIF model.}\label{fig:mainen}

>>>>

\includegraphics[width=\textwidth]{figures/replicating_MainenSejnowski1995.pdf} 
\caption{The timing of the spikes produced following the repetition of a step stimuli is less reproducible than that to a noisy stimulus. The stimulus is shown in the top row, while repetitions of a simulated Leaky Integrate-and-Fire neuron are shown in the second row (with membrane potential represented by  blue color when low hot yellow colors when depolarized). While this seems paradoxical at first sight, this is due to the use of the same \emph{frozen} noise at each repetition and highlight the highly reproducible pattern of spikes when it is driven by a highly dynamic input. See this \href{https://github.com/laurentperrinet/2022_UE-neurosciences-computationnelles/blob/master/C_MainenSejnowski1995.ipynb}{notebook} for a replication of this result using a simple LIF model.}\label{fig:mainen}
